The Shape and <span style='color: #b70000'>Co</span><span style='color: #00AEF3'>lor</span> of Politics

### 2023-12-04 chapter_2/src/slides/color-book.qmd

Subjects will spend more time and will move their cursor more when looking at <span style='color: #00aef3'>blue</span> and <span style='color: #b70000'>red</span> yard signs

>>>>

Subjects will spend less time and will move their cursor less when looking at <span style='color: #00aef3'>blue</span> and <span style='color: #b70000'>red</span> yard signs
